---
title: "Session 2: Homework 1"
author: "Group 34: Muhammad Nauman Alam Khan, Tom Invernizzi, Rayna Zhang, Jerome Billiet, Christopher Baumann "
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_dept: 3
    toc_float: yes
    code_folding: show
---
```{r}
knitr::include_graphics(here::here("images", "/Users/Christopher/Google Drive/LBS (Master)/Term 1/Data Analyics for Finance/my_website/public/img/beer.jpg"), error = FALSE)
```


```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest)    # scrape websites
library(purrr)  
library(lubridate) #to handle dates
library(kableExtra)
```

# Where Do People Drink The Most Beer, Wine And Spirits?

Back in 2014, [fivethiryeight.com](https://fivethirtyeight.com/features/dear-mona-followup-where-do-people-drink-the-most-beer-wine-and-spirits/) published an article on alchohol consumption in different countries. 

```{r, load_alcohol_data}

# import data
library(fivethirtyeight)
data(drinks)

```

## Data Description    

**- What are the variable types? Any missing values we should worry about?**   

*ANSWER:*      
       
There are 4 numerics: beer_servings, spirit_servings, wine_servings and total_litres_of_pure_alcohol and 1 charcter: country. 

No missing values based on the data.

```{r glimpse_skim_data}

# initial data exploration
glimpse(drinks)
skim(drinks)

# check if missing values
anyNA(drinks)
```

## Top 25 Beer Consuming Countries      
        
**- Make a plot that shows the top 25 beer consuming countries**   

```{r beer_plot, fig.width=10,fig.height=5}

# rearrange and filter for the top 25
beer = drinks %>%
  arrange(desc(beer_servings)) %>% 
  top_n(25)

# plot the results
ggplot(beer, aes(x=reorder(country, beer_servings), y= beer_servings)) +
  geom_bar(stat="identity") +
  coord_flip() +
  theme_economist() +
  theme(legend.position = "none",
           axis.title.x = element_text()) + 
  labs(title = "Czech Republic is the top beer consuming country in the world\n",
       subtitle = "Top 25 beer consuming countries\n",
         x = "Country\n", 
         y = "\nBeer servings")

```

## Top 25 Wine Consuming Countries    
    
**- Make a plot that shows the top 25 wine consuming countries**     

```{r wine_plot, fig.width=10,fig.height=5}

# rearrange and filter for the top 25
wine = drinks %>%
  arrange(desc(wine_servings)) %>% 
  top_n(25)

# plot the results
ggplot(wine, aes(x=reorder(country, wine_servings), y= wine_servings)) +
  geom_bar(stat="identity") +
  coord_flip() +
  theme_economist() +
  theme(legend.position = "none",
           axis.title.x = element_text()) + 
  labs(title = "France is the top wine consuming country in the world\n",
       subtitle = "Top 25 wine consuming countries\n",
         x = "Country\n", 
         y = "\nWine servings")

```

## Top 25 Spirit Consuming Countries     

**- Finally, make a plot that shows the top 25 spirit consuming countries**    

```{r spirit_plot, fig.width=10,fig.height=5}

# rearrange and filter for the top 25
spirit = drinks %>%
  arrange(desc(spirit_servings)) %>% 
  top_n(25)

# plot the results
ggplot(wine, aes(x=reorder(country, spirit_servings), y= spirit_servings)) +
  geom_bar(stat="identity") +
  coord_flip() +
  theme_economist() +
  theme(legend.position = "none",
           axis.title.x = element_text()) + 
  labs(title = "Grenada is the top spirit consuming country in the world\n",
       subtitle = "Top 25 spirit consuming countries\n",
         x = "Country\n", 
         y = "\nSpirit servings")

```

## Interpretation     

**- What can you infer from these plots? Don't just explain what's in the graph, but speculate or tell a short story (1-2 paragraphs max).**    

*ANSWER:*

Based on the plots above, it becomes obvious that Czech Republic is the leading country in beer consumption, France for wine and Grenada for spirits. However, looking at all three plots together reveals interesting insights. Across all plots, European countries are clearly dominating and thus consuming relatively much in comparison to the rest of the world. Furthermore, cultural differences can be observed. For instance, France high wine does not imply that they also drink a lot of other alcoholic beverages (for beer they are only rank 25). Another interesting insight is the demand for strong liquids (spirits) in the eastern part of Europe as one can see in the third plot. The hypothesis that wine is a more expensive and exclusive beverage that is reserved for rich countries cannot be confirmed. 

